The \dealii{} Library, Version 9.0

### 2018-04-07 9.0/paper.tex
Fix two typos.

\item
  A dedicated sundials module has been created to provide support for the
  SUNDIALS library. SUNDIALS is a SUite of Nonlinear and
  DIfferential/ALgebraic equations Solvers. ARKode, IDA, and KINSOL are
  supported. ARKode is a solver library that provides adaptive-step time
  integration. IDA is a package for the solution of differential-algebraic
  equations systems in the form $F(t,y,y')=0$. KINSOL is olver for nonlinear
  algebraic systems.

@@

\item
  A dedicated differentiation module has been created to provide support for
  automatic and symbolic differentiation. Automatic differentiation is a set of
  technique to evaluate the derivates of a function defined by a compute
  program. Currently the Adol-C and Sacado libraries are supported through a
  unified interface. In practice, this support means that Adol-c and Sacado
  data types can be used in the \texttt{FEValues} and \texttt{FEValuesViews}
  to represent degree-of-freedom values.

>>>>

\item
  A dedicated sundials module has been created to provide support for the
  SUNDIALS library. SUNDIALS is a SUite of Nonlinear and
  DIfferential/ALgebraic equations Solvers. ARKode, IDA, and KINSOL are
  supported. ARKode is a solver library that provides adaptive-step time
  integration. IDA is a package for the solution of differential-algebraic
  equations systems in the form $F(t,y,y')=0$. KINSOL is solver for nonlinear
  algebraic systems.

@@

\item
  A dedicated differentiation module has been created to provide support for
  automatic and symbolic differentiation. Automatic differentiation is a set of
  technique to evaluate the derivatives of a function defined by a compute
  program. Currently the Adol-C and Sacado libraries are supported through a
  unified interface. In practice, this support means that Adol-c and Sacado
  data types can be used in the \texttt{FEValues} and \texttt{FEValuesViews}
  to represent degree-of-freedom values.
